---
title: "Ancient Aliens"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    social: menu
    source_code: embed
    orientation: columns
    vertical_layout: fill
    css: styles.css
    
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(dplyr)
library(tidytext)
library(ggplot2)
library(scales)
library(tidyverse)

# Loading in all stemmed words and the airdate assocaited with the episode they are in. 
Stemmmed_Words_Time <- read.csv("./Data/Stemmmed_Words_Time.csv")
Stemmmed_Words_Time$AirDate = as.Date(Stemmmed_Words_Time$AirDate, "%Y-%m-%d")

# Preparing Word Choices
WordChoices <- data.frame('word' = sort(unique(Stemmmed_Words_Time$WordStem)))
WordChoices <- WordChoices %>%
  filter(!word %in% tidytext::stop_words)

# Loading In Word Count Data
Stem_Word_Props <- read.csv("./Data/Stem_Word_Props.csv")

# Loading In Word Count Data By Episode
Stem_Episode_Word_Props <- read.csv("./Data/Stem_Episode_Word_Props.csv")

# Loading In TF-IDF Dataset
Stem_Episode_tfidf <- read.csv("./Data/Stem_Episode_tfidf.csv")

#Topics and Gamma Datasets
Stem_Topics <- read.csv("./Data/Stem_Topics.csv")
Stem_Gamma <- read.csv("./Data/Stem_Gamma.csv")

# Loading in the Episode/Topic Datasets
Episode_Dates <- read.csv("./Data/Episode_Dates.csv")
Episode_Dates$Date = as.Date(Episode_Dates$Date, "%Y-%m-%d")

#Setting Colors
manual_colors = c('#005228', '#00651B', '#007707', '#0E8800', '#339900', '#67A922', '#95B844', '#BCC666',
                  '#888888', '#000000', '#666666', '#444444', '#222222', '#005228', '#00651B', '#007707', 
                  '#0E8800', '#339900', '#67A922', '#95B844', '#BCC666', '#888888', '#000000', '#666666', 
                  '#444444', '#222222')
```



Analysis Overview {}
====================================================================



### {data-height=200}
<B style='color: black;'>
<center><h2> Ancient Aliens, Conspiracy Theories, and Alt-Right Rhetoric: </h2>
<h3> Does conspiracy theory television promote extremist rhetoric? </h3>
<h5> Built and Prepared By: Jonathan Schlosser </h5></center>

<h4 style='text-indent: 50px;'>
This application was built to explore the scripts of the television show Ancient 
Aliens. Alt-right actors tend to exploit conspiracy spaces to radicalize individuals 
towards hateful beliefs. The work here questions the extent that alt-right rhetoric
may be present within one of the most recognizable conspiracy shows, Ancient Aliens. 


Topic modeling was used throughout these analyses. Topic modeling is a method 
for unsupervised classification of text documents to identify latent "topics". 
This app explores the results of a structural topic model and two LDA topic models 
(VEM and Gibbs) for the first 15 season of Ancient Aliens. These models are 
quite popular in the computational social science research community although they 
are not the most advanced natural language processing models available. 


The structural topic model was ultimately used in the analysis. This topic model 
allows for partial associations of topics to be considered and allows documents 
to appear in multiple topics. The LDA VEM model allows for this as well but models
the content differently and doesn't do too well with highly complex documents. The Gibbs
alternative is used mainly for short texts but was included here just as a comparison. 
The two LDA models did not reveal as clean of results as the STM approach. 

</h4>

<h4>
Some of the interesting findings include topics related to "alt-right" themes, including:

<ul>
  <li> Idolization of a Primordial Past </li>
    <ul>
      <li> Topic 3, Topic 13, Topic 14, Topic 15, Topic 18, Topic 20, Topic 24 </li>
    </ul>
  <li> Expressing Fears Around Difference </li>
    <ul>
      <Li> Topic 8, Topic 9, Topic 21, Topic 26 </li>
    </ul>
  <li> Suspicion of Government </li>
    <ul>
      <Li> Topic 2, Topic 10, Topic 12, Topic 19  </li>
    </ul>
  <li> A Belief in Warfare or Taking Action for Action's Sake</li>
    <ul>
      <Li> Topic 4, Topic 6, Topic 7  </li>
    </ul>
  <li> Worship of Technology </li>
    <ul>
      <Li> Topic 5, Topic 11, Topic 23, Topic 25  </li>
    </ul>
</ul>
</h4>
</B>


```{r}



```



Top Terms All Episodes {data-navmenu="Top Terms"}
====================================================================



```{r}
fillCol(height = 800, flex = c(NA, 1),
  inputPanel(
    selectizeInput("ResultLimit1", "Set Result Limit", choices = c(10, 20, 30, 40, 50), selected = 10),
    radioButtons("CountProp1", "Choose One:",
               c("Count" = "Count",
                 "Proportion" = "Proportion"), selected = "Count", inline = TRUE)
  ),
  plotOutput("WordCountPlot1", height = "100%")
)

output$WordCountPlot1 <- renderPlot({
  Stem_Word_Props %>% 
    top_n(as.integer(input$ResultLimit1), !!as.name(input$CountProp1)) %>%
    mutate(StemmedWord = reorder(StemmedWord, !!as.name(input$CountProp1))) %>%
    ggplot(aes(StemmedWord, !!as.name(input$CountProp1), fill = !!as.name(input$CountProp1))) +
    geom_col() +
    geom_text(aes(label = StemmedWord, y = 0), hjust = 0,
            color = "brown3", size = 5) +
    geom_text(aes(label = round(!!as.name(input$CountProp1), 6)), hjust = 1,
            color = "brown3", size = 5) +
    scale_fill_gradient(low = 'black', high = 'chartreuse1') +
    coord_flip() +
    theme_minimal(base_size = 18) +
    theme(axis.text.y=element_blank()) +
    labs(x = NULL, y = input$CountProp1, fill = "Title", title = paste("Top", input$ResultLimit1, "Terms Within All Episodes -", input$CountProp1))+
    guides(fill=FALSE)
})
```



Top Terms By Episode {data-navmenu="Top Terms"}
====================================================================



```{r}
fillCol(height = 800, flex = c(NA, 1),
  inputPanel(
    selectizeInput("Episode2", "Choose an episode:", choices = unique(Stem_Episode_Word_Props$EpisodeTitle)),
    selectizeInput("n2", "Set Result Limit", choices = c(10, 20, 30, 40, 50), selected = 10),
    radioButtons("CountProp2", "Choose One:",
               c("Count" = "Count",
                 "Proportion" = "Proportion"), selected = "Count", inline = TRUE)
  ),
  plotOutput("WordCountPlot2", height = "100%")
)

output$WordCountPlot2 <- renderPlot({
  Stem_Episode_Word_Props %>% 
    filter(EpisodeTitle == input$Episode2) %>%
    top_n(as.integer(input$n2), !!as.name(input$CountProp2)) %>%
    mutate(StemmedWord = reorder(StemmedWord, !!as.name(input$CountProp2))) %>%
    ggplot(aes(StemmedWord, !!as.name(input$CountProp2), fill = !!as.name(input$CountProp2))) +
    geom_col() +
    geom_text(aes(label = StemmedWord, y = 0), hjust = 0,
            color = "brown3", size = 5) +
    geom_text(aes(label = round(!!as.name(input$CountProp2), 6)), hjust = 1,
            color = "brown3", size = 5) +
    scale_fill_gradient(low = 'black', high = 'chartreuse1') +
    coord_flip() +
    theme_minimal(base_size = 18) +
    theme(axis.text.y=element_blank()) +
    labs(x = NULL, y = input$CountProp2, fill = "Title", title = paste("Top", input$n2, "Terms Within", input$Episode2, "-", input$CountProp2))+
    guides(fill=FALSE)
})
```



Episodes In Each Topic {data-navmenu="Topic Models"}
====================================================================



```{r}

fillCol(height = 800, flex = c(NA, 1), 
  inputPanel(
    radioButtons("ModelType4", "Choose a model",
               c("STM" = "STM",
                 "Gibbs" = "Gibbs",
                 "VEM" = "VEM"), selected = "STM", inline = TRUE),
    selectizeInput("topic4", "Choose a topic", choices = c(1:26)),
    selectizeInput("n4", "Set Result Limit", choices = c(10, 20, 30, 40, 50), selected = 10)
  ),
  plotOutput("TopicPlot4", height = "100%")
)


output$TopicPlot4 <- renderPlot({
   Stem_Gamma %>% 
    filter(Model == input$ModelType4) %>%
    filter(Topic == as.integer(input$topic4)) %>%
    top_n(as.integer(input$n4), Gamma) %>%
    mutate(EpisodeTitle = reorder(EpisodeTitle, Gamma)) %>%
    ggplot(aes(EpisodeTitle, Gamma, fill = Gamma)) +
    geom_col() +
    geom_text(aes(label = EpisodeTitle, y = 0), hjust = 0,
            color = "brown3", size = 5) +
    geom_text(aes(label = round(Gamma, 6)), hjust = 1,
            color = "brown3", size = 5) +
    scale_y_continuous(expand = c(0,0),
                       labels = percent_format()) +
    scale_fill_gradient(low = 'black', high = 'chartreuse1') +
    coord_flip() +
    theme_minimal(base_size = 18) +
    theme(axis.text.y=element_blank()) +
    labs(x = NULL, y = expression(gamma), fill = "Title", title = paste("Top", input$n4, "Episodes Within Topic", input$topic4, "-", input$ModelType4))+
    guides(fill=FALSE)
})

```



Terms In Each Topic {data-navmenu="Topic Models"}
====================================================================



```{r}

fillCol(height = 800, flex = c(NA, 1), 
  inputPanel(
    radioButtons("ModelType5", "Choose a model",
               c("STM" = "STM",
                 "Gibbs" = "Gibbs",
                 "VEM" = "VEM"), selected = "STM", inline = TRUE),
    selectizeInput("topic5", "Choose a topic", choices = c(1:26)),
    selectizeInput("n5", "Set Result Limit", choices = c(10, 20, 30, 40, 50), selected = 10)
  ),
  plotOutput("TopicPlot5", height = "100%")
)


output$TopicPlot5 <- renderPlot({
   Stem_Topics %>% 
    filter(Model == input$ModelType5) %>%
    filter(Topic == as.integer(input$topic5)) %>%
    top_n(as.integer(input$n5), Beta) %>%
    mutate(Term = reorder(Term, Beta)) %>%
    ggplot(aes(Term, Beta, fill = Beta)) +
    geom_col() +
    geom_text(aes(label = Term, y = 0), hjust = 0,
            color = "brown3", size = 5) +
    geom_text(aes(label = round(Beta, 6)), hjust = 1,
            color = "brown3", size = 5) +
    scale_y_continuous(expand = c(0,0),
                       labels = percent_format()) +
    scale_fill_gradient(low = 'black', high = 'chartreuse1') +
    coord_flip() +
    theme_minimal(base_size = 18) +
    theme(axis.text.y=element_blank()) +
    labs(x = NULL, y = expression(Beta), fill = "Title", title = paste("Top", input$n5, "Terms Within Topic", input$topic5, "-", input$ModelType5))+
    guides(fill=FALSE)
})

```



Term Timeline {data-navmenu="Timelines"}
====================================================================



```{r}

fillCol(height = 800, flex = c(NA, 1),
  inputPanel(
    selectizeInput("word3", "Choose A Word", choices = WordChoices, selected = "nazi", multiple = TRUE)
  ),
  plotOutput("WordTimePlot3", height = "100%")
)

output$WordTimePlot3 <- renderPlot({
  Stemmmed_Words_Time %>%
    group_by(AirDate) %>%
    count(WordStem, sort = TRUE) %>%
    filter(WordStem == input$word3) %>%
    ungroup() %>%
    mutate(WordStem = factor(WordStem)) %>%
    ggplot(aes(x = AirDate, y = n, group = WordStem, color = WordStem)) +
    geom_smooth(method = 'lm', show.legend = FALSE, se = FALSE) +  
    geom_point(show.legend = TRUE) +
    geom_smooth(aes(x = AirDate, y = n), method = 'lm', show.legend = FALSE, se = TRUE, 
                colour = 'red', fill = 'chartreuse1', inherit.aes = FALSE) +
    scale_colour_manual(values = manual_colors) +
    theme_minimal(base_size = 18) +
    labs(color = "Stemmed Word", x = NULL, y = 'Term Frequency', title = paste("Count Of Selected Term(s) Over Time"))
})



```



Topic Timeline {data-navmenu="Timelines"}
====================================================================
 
 
 
```{r}
fillCol(height = 600, flex = c(NA, 1),
  inputPanel(
    radioButtons("ModelType7", "Choose a model",
                 c("STM" = "STM",
                  "Gibbs" = "Gibbs",
                  "VEM" = "VEM"), selected = "STM", inline = TRUE),
    selectizeInput("topic7", "Choose A Topic", choices = unique(Episode_Dates$Topic), selected = 1, multiple = TRUE)
  ),
  plotOutput("topicPlot7", height = "100%")
)

output$topicPlot7 <- renderPlot({
  Episode_Dates %>%
    filter(Model == input$ModelType7) %>%
    filter(Gamma > 0.0001) %>%
    filter(Topic == as.integer(input$topic7)) %>%
    mutate(Topic = factor(Topic)) %>%
    ggplot(aes(x = Date, y = Gamma, group = Topic, color = Topic)) +
    geom_smooth(method = 'lm', show.legend = FALSE, se = FALSE) +  
    geom_point(show.legend = TRUE) +
    geom_smooth(aes(x = Date, y = Gamma), method = 'lm', show.legend = FALSE, se = TRUE, 
                colour = 'red', fill = 'chartreuse1', inherit.aes = FALSE) +
    scale_colour_manual(values = manual_colors) +
    scale_y_continuous(expand = c(0,0),
                       labels = percent_format()) +
    theme_minimal(base_size = 18) +
    labs(x = NULL, y = expression(gamma), title = paste("Selected Topic(s) Over Time"))
})

```
